\bf\mftitle

### 2011-03-01 doc/jInfer/xsdimport/xsdimport.tex
Fixed XSDImport according to first annotations.

Rule-trees are tree data structures, where vertices are instances of \code{Element} class and edges are the relations between them stored in \code{Regexp} instances within vertices. Every vertex is a rule by itself, so in order to obtain IG rules, one must extract all Elements from a rule-tree. Rule-trees are created by \code{DOMHandler}, described in section \ref{sect:domhandler}. The extraction is done by \code{DOMParser}, described in section \ref{sect::domparser}. Or alternatively, when parsing with SAX is selected, \code{SAXHandler} handles both processes.

@@

This module has several key roles in the process of importing XSD documents.\\

@@

Simmilar to the \code{Processor} implementations in the \code{BasicIGG} module, this is the core class of \code{XSDImporter} logic.
XSDProcessor registers itself into \emph{schema} input folder, \emph{xsd} file extension and declares it cannot handle other file extensions.\\
Class depends on NBP lookups (see \cite[section 4.1]{archdoc}) to find available parsers, and uses the selected parser to perform the import operation on defined files.
Initial grammar generated by this processor is considered \emph{complex} and should be followed by expansion (see \cite[section 4]{basiciggdoc}).

@@

\begin{verbatim}
List<Element> parse(final InputStream stream) throws XSDException;
\end{verbatim}

@@

- TODO explain the purpose of utility classes \\
- TODO describe every helper class in importer?

@@

\noindent \begin{tabular}{|l|l|} \hline
Module dependencies:   & Base \\ 
                       & XSDImporter \\ \hline
Public packages:       & none \\ \hline
\end{tabular}
\\
This module implements the import functionality using API from Xerces DOM parser. Its structure is very simple, all classes are grouped in one main package, relying on utility classes from \code{XSDImporter} module mentioned before.

@@

BuildRuleSubtree is the most important method. It is divided into four logical parts
\begin{enumerate}
	\item Creates an \code{Element} instance with appropriate parameters (occurences, metadata, etc.).
	\item Inspects the given tag and sets parameters for subnodes \code{Regexp}.
	\item Recursively creates rule-subtrees for its children.
	\item Finalizes the instance by checking for extra conditions.
\end{enumerate}

@@

\noindent \begin{tabular}{|l|l|} \hline
Module dependencies:   & Base \\ 
                       & XSDImporter \\ \hline
Public packages:       & none \\ \hline
\end{tabular}
\\
This module implements the import functionality using API of a standard SAX parser. Its structure is divided in two packages. Package \code{cz.cuni.mff.ksi.jinfer.xsdimportsax} holds the main parsing logic, while package \code{cz.cuni.mff.ksi.jinfer.xsdimportsax.utils} contains two utility classes. Both \code{SAXAttributeData} and \code{SAXDocumentElement} serve as wrappers for tag attributes and tags of the input Schema file during parsing, to ease the process of extracting data from them.

@@

@@

\subsection{Data Flow using SAX parser}

@@

\section{Known issues and limitations}

@@

When the complete definition of \code{fileType} is read, this type is also only added to a list of known types, no dependencies are retrospectively resolved.
The reason for it lies in one-pass approach of SAX parser. In future versions, we are planning to resolve this issue by creating dependency trees of \code{complexType} tag definitions. However, it will make the parsing algorithm more time and memory expensive.

@@

\section{Extensibility}

>>>>

Rule-trees are tree data structures, where vertices are instances of \code{Element} class and edges are the relations between them stored in \code{Regexp} instances within vertices. Every vertex is a rule by itself, so in order to obtain IG rules, one must extract all Elements from a rule-tree. Rule-trees are created by \code{DOMHandler}, described in subsection \ref{sect:domhandler}. The extraction is done by \code{DOMParser}, described in subsection \ref{sect:domparser}. Or alternatively, when parsing with SAX is selected, \code{SAXHandler} handles both processes.

Life cycle of rule-trees is apparent from section \ref{sect:dataflow}.

@@

\noindent This module has several key roles in the process of importing XSD documents.\\

@@

Similar to the \code{Processor} implementations in the \code{BasicIGG} module, this is the core class of \code{XSDImporter} logic.
\code{XSDProcessor} registers itself into \emph{schema} input folder, \emph{xsd} file extension and declares it cannot handle other file extensions.\\
Class depends on NBP lookups (see \cite[section 4.1]{archdoc}) to find available parsers, and uses the selected parser to perform the import operation on defined files.
Initial grammar generated by this processor is considered \emph{complex} and should be followed by expansion (see \cite[section 4]{basiciggdoc}).

@@

\begin{verbatim}
List<Element> parse(InputStream stream) throws XSDException;
\end{verbatim}

@@

\paragraph{Built-in data types}

A special class is designed to contain all built-in data types supported by XSD language. Both built-in primitive types and built-in derived types are recognized. For a complete list, please see our JavaDoc documentation for \code{XSDBuiltInDataTypes} class. These types are contained using instances of \code{SimpleData} class, as described in \cite[section 2.2]{archdoc}.

@@

\noindent \begin{tabular}{|l|l|} \hline
Module dependencies:   & Base \\ 
                       & XSDImporter \\ \hline
Public packages:       & none \\ \hline
\end{tabular}
\\

\noindent This module implements the import functionality using API from Xerces DOM parser. Its structure is very simple, all classes are grouped in one main package, relying on utility classes from \code{XSDImporter} module mentioned before.

@@

The most important method is \code{buildRuleSubtree()}. It is divided into four logical parts.
\begin{enumerate}
	\item Creates an \code{Element} instance with appropriate parameters (occurences, metadata, etc.).
	\item Inspects the given tag and sets parameters for subnodes \code{Regexp}.
	\item Recursively creates rule-subtrees for its children.
	\item Finalizes the instance by checking for extra conditions.
\end{enumerate}

Signature of the method is:
\begin{verbatim}
private Pair<Element, RegexpInterval> buildRuleSubtree(
	org.w3c.dom.Element currentNode,
	List<String> context,
	List<org.w3c.dom.Element> visited) throws XSDException
\end{verbatim}

Method takes current node, which will be returned as root \code{Element} node (first value of the returned pair) of this subtree, and creates an entire rule-tree below it by recursively calling itself, as mentioned in step 3. Context parameter holds the list of names of nodes that create unique path from actual root of the schema document to the current node. Visited parameter lists references to instances of \code{Element} that were visited on this path. When handling \emph{attribute} tags, context needs to be passed along, but list of visited nodes does not.

@@

\noindent \begin{tabular}{|l|l|} \hline
Module dependencies:   & Base \\ 
                       & XSDImporter \\ \hline
Public packages:       & none \\ \hline
\end{tabular}
\\

\noindent This module implements the import functionality using API of a standard SAX parser. Its structure is divided in two packages. Package \code{cz.cuni.mff.ksi.jinfer.xsdimportsax} holds the main parsing logic, while package \code{cz.cuni.mff.ksi.jinfer.xsdimportsax.utils} contains two utility classes. Both \code{SAXAttributeData} and \code{SAXDocumentElement} serve as wrappers for tag attributes and tags of the input Schema file during parsing, to ease the process of extracting data from them.

@@

Sax handler implements methods in response to the events generated by the underlying SAX parser API.
Similar to its counterpart, \code{DOMHandler}, this class holds most on the logic for importing a Schema.
It works by keeping current tree branch, which is being parsed, on a stack. Adding current node to the parent on top of the stack as current tag finishes.

@@

\subsection{Data Flow using SAX parser} \label{sect:dataflow}

@@

\section{Known issues and limitations} \label{sect:issues}

@@

When the complete definition of \code{fileType} is read, this type is also only added to a list of known types, no dependencies are retrospectively resolved.
The reason for it lies in one-pass approach of SAX parser. In future versions, we are planning to resolve this issue by creating dependency trees of \code{complexType} tag definitions. However, it will make the parsing algorithm more time and memory expensive.\\

@@

\section{Extensibility} \label{sect:extensibility}
